---
html_document: null
keep_md: yes
output:
  html_document:
    theme: cerulean
title: 'Reproducible Research: Peer Assessment 1'
---


##### Loading required R Packages
  
```{r, echo=TRUE}
library("knitr")
library("markdown")
library("utils")
library("ggplot2")
library("stats")
```


##### Loading and preprocessing the data

```{r, echo=TRUE}
if(!exists("activity.csv")) {unzip("activity.zip")}
if(!exists("ActivityData")) {ActivityData<<-read.csv("activity.csv")}
ActivityData$date<-strptime(ActivityData$date, format = "%Y-%m-%d")
head(ActivityData)
```

##### Histogram of the total number of steps taken each day.
```{r}
Daily<-aggregate(steps ~ as.character(date), data = ActivityData, FUN=sum, na.rm=TRUE)
hist(Daily$steps, xlab="Number of Steps", ylab="Number of Days", main= "Histogram - (Days/Steps)")
```

##### What is mean total number of steps taken per day?
##### What is median total number of steps taken per day?
```{r,echo=TRUE}
## Caluclates the mean total number of steps taken per day
StepsMean<-round(mean(Daily$steps))
## Caluclates the median number of steps taken per day
StepsMedian<-round(median(Daily$steps))


```

##### As calculated  mean of steps  taken per day is 10766 and the median is 10765.

##### What is the average daily activity pattern?

``````{r,echo=TRUE}

```


##### Imputing missing values



##### Are there differences in activity patterns between weekdays and weekends?
